---
title: "SRT411A0"
output: word_document
---
---
GitHub Username: Squatchinator01
---

---
Link to the Assignment Document: https://cran.r-project.org/doc/contrib/Torfs+Brauer-Short-R-Intro.pdf
---


## Introduction

In this assignment, you were to read the document "A (very) Short Introduction to R" and complete all 14 of the "To-Do" Tasks that were at the end of each section. Then make a report using RMarkdown and publish it on GitHub. 

## Task 1 

```{r}
((2015-2014)/(2014-1997))*100 
```

## Task 2

```{r}
a <- 2015-2014
b <- 2014-1997
c <- 100 
a/b *c 
```

## Task 3 

```{r}
vector <- c(4, 5, 8, 11) 
sum(vector)
```

## Task 4 

```{r}
plot(rnorm(100)) 
```

## Task 5 

```{r}
help(sqrt) 
```

## Task 6

```{r}
source("firstscript.R")
```

## Task 7 

```{r}
P = seq(from = 31, to = 60, by = 1) 
Q = matrix(P, ncol = 5, nrow = 6) 
P 
```

## Task 8 

```{r}
x1 = seq(from = 1, to = 100, by = 1)
x2 = seq(from = 101, to = 200, by = 1) 
x3 = seq(from = 201, to = 300, by = 1) 
 t = data.frame(a = 1, b = x1 + x2, c = x1 + x2 + x3) 
plot(t)  
```

## Task 9

```{r}
x1 = seq(from = 1, to = 100, by = 1)
x2 = seq(from = 101, to = 200, by = 1) 
x3 = seq(from = 201, to = 300, by = 1) 
t = data.frame(a = 1, b = x1 + x2, c = x1 + x2 + x3)   
plot(t$a, type="l", ylim=range(t),
lwd=3, col=rgb(1,0,0,0.3))
lines(t$b, type="s", lwd=2,
col=rgb(0.3,0.4,0.3,0.9))
points(t$c, pch=20, cex=4,
col=rgb(0,0,1,0.3))  
```

## Task 10

```{r}
read <- read.table(file = "tst1.txt", header = TRUE)
d <- read$g*5 
write.table(d, file = "tst2.txt", row.names = FALSE)
```

## Task 11 

```{r}
sqrt(mean(rnorm(100)))
```

## Task 12

```{r}
date <- strptime( c("22052017", "25122016"), format = "%d%m%Y")
presents <- c(2, 6)
plot(date, presents)  
```

## Task 13

```{r}
vector <- seq(from = 1, to = 100, by = 1) 
s=c()
for(i in 1:100)
{
  if(vector[i]<5)
  {
    s[i]=vector[i]*5;
  }
  else if(vector[i]>90)
  {
    s[i]=vector[i]*10;
  }
  else
  {
    s[i]=vector[i]*0.1;
  }
}
s 
```

## Task 14 

```{r}
fun= function(arg1,arg2 )
{
  vector[i]=arg1[i];
  for(i in length(vector))
  {
    
  }
} 
```

## Resources

https://www.dataquest.io/blog/how-to-share-data-science-portfolio/
https://www.dataquest.io/blog/how-to-share-data-science-portfolio/
https://nicercode.github.io/guides/reports/
http://kbroman.org/knitr_knutshell/pages/markdown.html
https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf 